Level-Set method on \texttt{p4est}

### 2015-06-26 paper/tex/scaling_results.tex
Added my modifications - Ready for submission

Table \ref{tab:semilagrangian} illustrates the dependence of the number of sub-iterations required to build the grid on the CFL number; as the CFL is increased, the interface travels a farther distance, which necessitates more sub-iterations to generate the grid. Note that the apparent dependence on the number of processes is most likely due to round-off errors during the interpolation and/or backtracking steps. Figures \ref{fig:semilagrangian_small} and \ref{fig:semilagrangian_large} illustrate the scalability of the algorithm for the small and large problems, respectively. To enable meaningful comparisons between different CFL numbers and number of processes, the maximum time has been scaled by the number of sub-iterations required for the grid construction as reported in Table \ref{tab:semilagrangian}. For both problems, excellent scalability is observed for $\text{CFL} = 1$ and $\text{CFL} = 10$. The algorithm even shows good scalability when taken to the extreme, i.e. for $\text{CFL} = 100$.

>>>>

Unlike many existing applications where the mesh is changed infrequently, our semi-Lagrangian algorithm requires several sub-iterations of the refinement and coarsening operations. As a result, it is expected that refinement and coarsening steps constitute a significant portion of the total runtime which puts stringent scalability requirements on these algorithms. We refer the interested reader to section 3.2 of \cite{Burstedde;Wilcox;Ghattas:11:p4est:-Scalable-Algo} for detailed description of scalable refinement and coarsening algorithms in \texttt{p4est}.

Table \ref{tab:semilagrangian} illustrates the dependence of the number of sub-iterations required to build the grid on the CFL number; as the CFL is increased, the interface travels a farther distance, which necessitates more sub-iterations to generate the grid. Figures \ref{fig:semilagrangian_small} and \ref{fig:semilagrangian_large} illustrate the scalability of the algorithm for the small and large problems, respectively. To enable meaningful comparisons between different CFL numbers and number of processes, the maximum time has been scaled by the number of sub-iterations required for the grid construction as reported in Table \ref{tab:semilagrangian}. For both problems, excellent scalability is observed for $\text{CFL} = 1$ and $\text{CFL} = 10$. The algorithm even shows good scalability when taken to the extreme, i.e. for $\text{CFL} = 100$.
